### 2014-07-07 ms/ms.Rmd
Spelling, short link
dataMashR update: Use lower case for names of data dictionary. Closes 128

vars <- setdiff(var.def$Variable[var.def$Type == "numeric"], c("map","mat","lai","age"))
```

@@

We (D.S. Falster and R.A. Duursma, with the help of D.R. Barneche, R.G. FitzJohn and A. Vårhammer) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M. Ishihara and focussing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$studyName))` different published and unpublished studies.

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
x <-daply(var.def, 1, function(x)
		paste0("* ", x$Variable,
    "\n\t- Type: ", x$Type,
		"\n\t- Label: ", x$label,
		"\n\t- Description: ", x$Description,
		"\n\t- Units: ", gsub(".","/", x$UnitsMD, fixed=TRUE)
		))

writeLines(x[var.def$Variable])
```

>>>>

vars <- setdiff(var.def$variable[var.def$type == "numeric"], c("map","mat","lai","age"))
```

@@

We (D.S. Falster and R.A. Duursma, with the help of D.R. Barneche, R.G. FitzJohn and A. Vårhammar) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M. Ishihara and focussing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$studyName))` different published and unpublished studies.

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
x <-daply(var.def, 1, function(x)
		paste0("* ", x$variable,
    "\n\t- Type: ", x$type,
		"\n\t- Label: ", x$label,
		"\n\t- Description: ", x$description,
		"\n\t- Units: ", gsub(".","/", x$unitsMD, fixed=TRUE)
		))

writeLines(x[var.def$variable])
```
